---
title: "setup"
author: "Richard Ramsey"
date: '2022-05-11'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This file tries to load packages and then update the renv lock.file and see if it can push successfully to git and github, so that the renv.lock file is also under version control via git.

## initialise renv ##

This should be done already if when you created the R project, you ticked the renv button. If not, it renv will need initialising. 

```{r initialise-renv}
# renv::init()
```

## restore renv from a previously saved lock file ##

```{r restore-renv}
renv::restore()
```

## load packages that we will be using ##

first time, load some packages (and then later, load a new package just to test functionality)

```{r}
# install or load packages
options(repos="https://cran.rstudio.com" )
if (!require("install.load")){install.packages("install.load")} 
install_load("here", "tidyverse", "RColorBrewer", "patchwork")
```

## do some wrangling ##

```{r load-some-data}
data <- as_tibble(mtcars) %>% 
  mutate(cyl = factor(cyl))
head(data)
str(data)
```

## plot some stuff ##

```{r plot}
p1 <- ggplot(data, 
             aes(x=hp, y=mpg, colour=cyl, shape=cyl)) +
  geom_point() +
  theme_bw() +
  scale_colour_brewer(palette = "Dark2") +
  facet_wrap(~cyl)
p1

ggsave("figures/p1.jpeg")
```

## take a snapshot ##

```{r}
renv::snapshot()
```


close down and renv::restore(). Yes, all worked well.



## load an additional package ##

second time, when the packages will be updated via the addition of brms.

```{r}
# install or load packages
options(repos="https://cran.rstudio.com" )
if (!require("install.load")){install.packages("install.load")} 
install_load("brms")
```

## run a simple model using brms ##

```{r}
b1 <- brm(mpg ~ 1 + hp,
          data = data, family = gaussian,
          file = "models/b1")
summary(b1)
```

## take a snapshot ##

```{r}
renv::snapshot()
```

Yes, all seems to work ok and the renv.lock file is updated, git tracks the change and we push it to GitHub.

## print session info ##

```{r session-info}
sessionInfo()
```